SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-03 scipy-1.0/paper.tex
alternative language breakdown figure

Python, Cython, Fortran, C and C++ are the programming languages used to
implement scientific algorithms in the SciPy library. An analysis of our 
codebase using the \texttt{linguist} library\cite{linguistref} provides a 
detailed breakdown as \% composition by programming language in 
SciPy (Figure~\ref{fig:linguist}).

\begin{figure}[H]
    \centering

    \begin{tikzpicture}[font=\sffamily]
    \begin{axis}[height=6cm, width=10cm,
    ybar, ymax=60, ymin=0,bar width=1cm,
    ylabel={\% of Scipy codebase},
    ytick={0,20,...,60},
    axis lines*=left,
    axis y line shift=0pt,
    enlarge x limits=0.15,
    symbolic x coords={py,f,c,cy,cpp},
    xticklabels={Python,FORTRAN,C,Cython,C++},
    ticklabel style={align=center,font=\sffamily\small,
    /pgf/number format/assume math mode=true},
    xtick=data,
    nodes near coords,
    nodes near coords style={/pgf/number format/assume math mode=true}
    ]
    \addplot coordinates {(py,49.5) (f,25.6) (c,19.5) (cy, 3.0) (cpp,2.3)};
    \end{axis}
    \end{tikzpicture}
    \caption{The breakdown of programming languages used in the
             SciPy library determined using the linguist library.
    	 Small ($<0.5 \%$) amounts of TeX, Matlab, Shell,
    	 and Makefile are excluded for clarity and mostly
    	 provide supporting roles in tests, building, and
    	 documentation.}
    \label{fig:linguist}
\end{figure}

@@

@@

\texttt{scipy.sparse} offers seven sparse matrix data structures,
also known as sparse formats. The most important ones are the row- 
and column-compressed formats (CSR and CSC, respectively). 
These offer fast major-axis indexing and fast matrix-vector multiplication,
and are used heavily throughout SciPy and dependent packages.

Over the last three years, our sparse matrix handling internals have been
rewritten and performance has been improved. Iterating over and slicing of CSC
and CSR matrices is now faster by up to 35\% (Figure~\ref{fig:sparse-iter}),
 and the coordinate (COO)/ diagonal (DIA) to CSR / CSC matrix format
conversions are now faster (Figure~\ref{fig:sparse-conv}). Importantly,
SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing the
low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

@@

\subsubsection*{cKDTree}

@@

\subsubsection*{Test suite}
\label{sec:testsuite}

>>>>

Python, Cython, Fortran, C and C++ are the programming languages used to
implement scientific algorithms in the SciPy library. An analysis of our code
base using the \texttt{linguist} library\cite{linguistref} provides a 
detailed breakdown as \% composition by programming language in 
SciPy (Figure~\ref{fig:linguist}).

\begin{figure}[H]
    \centering
		\includegraphics[width=\textwidth]{static/composition}
    \caption{The breakdown of programming languages used in the
             SciPy library determined using the linguist library.
    	 Small ($<0.5 \%$) amounts of TeX, Matlab, Shell,
    	 and Makefile are excluded for clarity and mostly
    	 provide supporting roles in tests, building, and
    	 documentation.}
    \label{fig:linguist}
\end{figure}

@@

\subsubsection*{\texttt{cKDTree}}

@@

\texttt{scipy.sparse} offers seven sparse matrix data structures,
also known as sparse formats. The most important ones are the row- 
and column-compressed formats (CSR and CSC, respectively). 
These offer fast major-axis indexing and fast matrix-vector multiplication,
and are used heavily in scikit-learn.

Over the last three years our sparse matrix handling internals have been
rewritten and performance has been improved. Iterating over and slicing of CSC
and CSR matrices is now faster by up to 35\% (Figure~\ref{fig:sparse-iter}),
 and the COO / DIA to CSR / CSC matrix format
conversions are now faster (Figure~\ref{fig:sparse-conv}). Importantly,
SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing the
low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

@@

@@

\subsubsection*{Test suite}
